Automatic Matching of Bullet Lands

### 2016-01-17 imaging-paper.Rnw
A couple typos

Besides resulting in a probabilistic quantification of matches, random forests also provide an assessment of the importance of each of the features derived from the bullets' 3D topological surface measurements. Figure~\ref{fig:importance} shows an overview of the importance of each variable measured as the mean decrease in the Gini index when the variable in question is included in a tree (for the exact values please refer to supplement section~\ref{supp:randomforest}). 
\begin{figure}
<<echo=FALSE, fig.width=7, fig.height=2, out.width='.7\\textwidth'>>=
imp <- data.frame(importance(rtrees))
imp$Variable <- row.names(imp)
imp$Variable[c(7,8)] <- c("#matches", "#non-matches")
imp1 <- subset(imp, !(Variable %in% c("x1", "sd.D", "S")))
imp2 <- subset(imp, Variable %in% c("x1", "sd.D", "S"))
qplot(MeanDecreaseGini,1, data=imp, geom="point") + 
  geom_text(aes(y=1.2, label=Variable), angle=45, hjust=0, data=imp1) + 
  geom_text(aes(y=0.8, label=Variable), angle=-45, hjust=0, data=imp2) + 
  ylim(c(0, 2.75)) + theme_bw() + ylab("") +
  theme(axis.ticks.y=element_blank(), axis.text.y=element_blank(),
        panel.grid.major.y=element_blank(), panel.grid.minor.y=element_blank()) +
  xlab("Importance (mean decrease in Gini index)")
@
\caption{\label{fig:importance}Importance of features in the random forest. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree.}
\end{figure}

@@

\hh{Besides including results from known matches against known non-matches, we can increase the number of comparisons in the Hamby study to include all possible land-to-land comparisons. This effectively doubles the number of data points available. Comparisons not previously included in fitting the random forest can also be used as an additional source for assessing error rates.  Results for this and a more detailed discussion can be found in supplement section~\ref{supp:extended}.}

>>>>

Besides resulting in a probabilistic quantification of matches, random forests also provide an assessment of the importance of each of the features derived from the bullets' 3D topological surface measurements. Figure~\ref{fig:importance} shows an overview of the importance of each variable measured as the mean decrease in the Gini index when the variable in question is included in a tree (for the exact values please refer to Supplement section~\ref{supp:randomforest}). 
\begin{figure}
<<echo=FALSE, fig.width=7, fig.height=2, out.width='.7\\textwidth'>>=
imp <- data.frame(importance(rtrees))
imp$Variable <- row.names(imp)
imp$Variable[c(7,8)] <- c("#matches", "#non-matches")
imp1 <- subset(imp, !(Variable %in% c("x1", "sd.D", "S")))
imp2 <- subset(imp, Variable %in% c("x1", "sd.D", "S"))
qplot(MeanDecreaseGini,1, data=imp, geom="point") + 
  geom_text(aes(y=1.2, label=Variable), angle=45, hjust=0, data=imp1) + 
  geom_text(aes(y=0.8, label=Variable), angle=-45, hjust=0, data=imp2) + 
  ylim(c(0, 2.75)) + theme_bw() + ylab("") +
  theme(axis.ticks.y=element_blank(), axis.text.y=element_blank(),
        panel.grid.major.y=element_blank(), panel.grid.minor.y=element_blank()) +
  xlab("Importance (mean decrease in Gini index)")
@
\caption{\label{fig:importance}Importance of features in the random forest. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree.}
\end{figure}

@@

\hh{Besides including results from known matches against known non-matches, we can increase the number of comparisons in the Hamby study to include all possible land-to-land comparisons. This effectively doubles the number of data points available. Comparisons not previously included in fitting the random forest can also be used as an additional source for assessing error rates.  Results for this and a more detailed discussion can be found in Supplement section~\ref{supp:extended}.}
